---
title: "Button"
description: "Displays a button or a component that looks like a button."
---

```{r, include = FALSE}
library(shiny)
library(shinyblocks)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Button

Displays a button or a component that looks like a button.

## Installation

Add `shinyblocks` to your project dependencies:

```r
# If not already installed
# remotes::install_github("nvelden/shinyblocks")
```

## Usage

```r
library(shinyblocks)

block_button("Button", variant = "default")
```

## Examples

### Basic

A basic button with default styling.

<div class="sb-component-preview">
```{r, echo=FALSE, results="asis"}
cat(as.character(block_button("Button")))
```
</div>
<div class="sb-component-code-title">Code</div>
```r
block_button("Button")
```

### Variants

Use the `variant` prop to change the visual style of the button.

<div class="sb-component-preview">
```{r, echo=FALSE, results="asis"}
cat(as.character(htmltools::tagList(
  block_button("Default"),
  block_button("Secondary", variant = "secondary"),
  block_button("Outline", variant = "outline"),
  block_button("Ghost", variant = "ghost"),
  block_button("Destructive", variant = "destructive"),
  block_button("Link", variant = "link")
)))
```
</div>
<div class="sb-component-code-title">Code</div>
```r
block_button("Default")
block_button("Secondary", variant = "secondary")
block_button("Outline", variant = "outline")
block_button("Ghost", variant = "ghost")
block_button("Destructive", variant = "destructive")
block_button("Link", variant = "link")
```

### Sizes

Use the `size` prop to change the size of the button.

<div class="sb-component-preview">
```{r, echo=FALSE, results="asis"}
cat(as.character(htmltools::tagList(
  block_button("Small", size = "sm"),
  block_button("Default"),
  block_button("Large", size = "lg")
)))
```
</div>
<div class="sb-component-code-title">Code</div>
```r
block_button("Small", size = "sm")
block_button("Default", size = "default")
block_button("Large", size = "lg")
```

### With Icons

You can add icons to the button and control their position.

<div class="sb-component-preview">
```{r, echo=FALSE, results="asis"}
cat(as.character(htmltools::tagList(
  block_button("Search", icon = "search"),
  block_button("Next", icon = "arrow-right", icon_position = "inline-end")
)))
```
</div>
<div class="sb-component-code-title">Code</div>
```r
block_button("Search", icon = "search")
block_button("Next", icon = "arrow-right", icon_position = "inline-end")
```
